---
title: "lab-07-simpsons.Rmd"
author: "Sara Tlal "
date: "20 March 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r load_libraries, message=FALSE}
library(tidyverse) 
library(mosaicData)
```


## Exercises


1.  
```{r whickam}
 view(Whickham)
```
    
Your answer:
observational , Because they notice a person's health status after a period of time
2.  
```{r observations}
nrow(Whickham)
```

Your answer;
1314 ,represent recorded participants’ age, smoking status at baesline
3.  

```{r number_variables}
ncol(Whickham)
```

Your answer:  


```{r var_type}
 class(Whickham$age)
 class(Whickham$smoker)
  class(Whickham$outcome)
```

Your answer: 
3 , age (Numerical) , smoker and outcome are categorical
age (integer) , smoker and outcome are (factor)

```{r plot_outcome}
ggplot(Whickham, aes(x = outcome)) +
  geom_bar()
```


```{r plot_smoker}
ggplot(Whickham, aes(x = smoker)) +
  geom_bar()
```

```{r plot_age}
ggplot(Whickham, aes(x = age)) +
  geom_bar()
```


4. 
I expect the health will be worser and may be the person will be died after while ,if he keeping somke

```{r plot_smokeVSincome_1}
ggplot(data=Whickham, aes(x=smoker, y=outcome, color=outcome)) + geom_bar(stat="identity")
```

Knit, commit, and push to github.

5. 

```{r plot_smokeVSincome_2}
Whickham %>%
  count(smoker, outcome)
```

6.

```{r age_cat}

```

7. 

```{r plot_smokeVSincome_3}

```

Knit, commit, and push to github.